The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-04 src/ms.tex
url to href

The \astropypkg core package was one of the first large, open-source \python
packages developed for astronomy and provides, among other things, software
functionality for reading and writing astronomy-specific data formats (e.g.,
FITS), transforming and representing astronomical coordinates, and representing
and propagating physical units in code.
An early description of the core functionality in \astropypkg can be found in
the first \astropy paper \citep{astropy:2013} or in detail in the core package
documentation.\footnote{\url{https://docs.astropy.org/}}
The codebase in the \astropypkg core package is now largely stable, in that the
software interface does not change without sufficient and significant
motivation, and the addition of new features into the core package has slowed
as compared to the first years of its development.
This is largely driven by the fact that the core package now represents just one
piece of the broader astronomy \python context, and new feature development
is now happening in more specialized packages that are expanding the
capabilities of the \astropy ecosystem by building on top of the foundations
laid by the \astropypkg core package.
Because of this natural expansion, the name \astropy has grown in scope beyond a
single \python library to become ``the Astropy Project.''

>>>>

The \astropypkg core package was one of the first large, open-source \python
packages developed for astronomy and provides, among other things, software
functionality for reading and writing astronomy-specific data formats (e.g.,
FITS), transforming and representing astronomical coordinates, and representing
and propagating physical units in code.
An early description of the core functionality in \astropypkg can be found in
the first \astropy paper \citep{astropy:2013} or in detail in the
\href{https://docs.astropy.org/}{core package documentation}.
The codebase in the \astropypkg core package is now largely stable, in that the
software interface does not change without sufficient and significant
motivation, and the addition of new features into the core package has slowed
as compared to the first years of its development.
This is largely driven by the fact that the core package now represents just one
piece of the broader astronomy \python context, and new feature development
is now happening in more specialized packages that are expanding the
capabilities of the \astropy ecosystem by building on top of the foundations
laid by the \astropypkg core package.
Because of this natural expansion, the name \astropy has grown in scope beyond a
single \python library to become ``the Astropy Project.''
